Add Plant Functional Type (PFT) labels

### 2021-04-23 R/add_plant_functional_type.Rmd
finished initial labeling and checking the  col values

  else if(genusSpecies == "Bourreria sp."){
    taxon_pft_lookup$pft_MRA[i] = "NA"
    taxon_pft_lookup$pft_MODIS[i] = "NA"
    taxon_pft_lookup$phenology[i] = "NA"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "strongbark"
    taxon_pft_lookup$commonName[i] = "varied genus"}

@@

  else if(genusSpecies == "Juniperus osteosperma"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen_needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "Utah juniper"
    taxon_pft_lookup$comments[i] = "scale-like needle leaves"}

  else if(genusSpecies == "Juniperus virginiana"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen_needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf" 
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "red cedar"
    taxon_pft_lookup$comments[i] = "scale-like needle leaves"}

@@

  else if(genusSpecies == "Quercus falcata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "southern red oak"}

  else if(genusSpecies == "Quercus geminata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "sand live oak"}

  else if(genusSpecies == "Quercus hemisphaerica"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "Darlington oak"}

  else if(genusSpecies == "Quercus laevis"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "turkey oak"}

  else if(genusSpecies == "Quercus laurifolia"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "laurel oak"}

  else if(genusSpecies == "Quercus lyrata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "overcup oak"}

  else if(genusSpecies == "Quercus macrocarpa"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "bur oak"}

  else if(genusSpecies == "Quercus margaretta"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "sand post oak"}

  else if(genusSpecies == "Quercus marilandica"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "blackjack oak"}

  else if(genusSpecies == "Quercus michauxii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "swamp chestnut oak"}

  else if(genusSpecies == "Quercus montana"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "chestnut oak"}

  else if(genusSpecies == "Quercus muehlenbergii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "chinquapin oak"}

  else if(genusSpecies == "Quercus nigra"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "water oak"}

  else if(genusSpecies == "Quercus pagoda"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "cherrybark oak"}

  else if(genusSpecies == "Quercus phellos"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "willow oak"}

  else if(genusSpecies == "Quercus rubra"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "northern red oak"}

  else if(genusSpecies == "Quercus shumardii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "Shumard's oak"}

  else if(genusSpecies == "Quercus sp."){
    taxon_pft_lookup$pft_MRA[i] = "NA"  # apparently there are evergreen oak species? 
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "oak"}

  else if(genusSpecies == "Quercus stellata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "post oak"}

  else if(genusSpecies == "Quercus velutina"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "black oak"}

  else if(genusSpecies == "Quercus virginiana"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "live oak"}

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft_MRA[i] = "NA"     #  spreading shrub or small tree reaching 25 to 30 feet
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

  else if(genusSpecies == "Rhus aromatica"){
    taxon_pft_lookup$pft_MRA[i] = "woody_shrub"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "fragrant sumac"}

  else if(genusSpecies == "Rhus glabra"){
    taxon_pft_lookup$pft_MRA[i] = "woody_shrub"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "smooth sumac"}

  else if(genusSpecies == "Robinia pseudoacacia"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "black locust"}

  else if(genusSpecies == "Sassafras albidum"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest" # deciduous shrub or tree. trees are 9 to 18 m
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "sassafras"}

  else if(genusSpecies ==  "Sassafras sp."){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "sassafras"}

  else if(genusSpecies == "Sideroxylon lanuginosum"){
    taxon_pft_lookup$pft_MRA[i] = "NA" # deciduous multi-trunked tall shrub or medium-sized tree to 48ft or more
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "gum bully"}

  else if(genusSpecies == "Symplocos sp."){
    taxon_pft_lookup$pft_MRA[i] = "NA"  # "deciduous or evergreen shrub or tree"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "sweetleaf"}

  else if(genusSpecies == "Taxus brevifolia"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "Pacific yew"}

  else if(genusSpecies == "Tetradium daniellii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "bee-bee tree"}

  else if(genusSpecies == "Triadica sebifera"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "Chinese tallow"}

  else if(genusSpecies == "Tsuga canadensis"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "eastern hemlock"}

  else if(genusSpecies == "Tsuga heterophylla"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "western hemlock"}

  else if(genusSpecies == "Ulmus alata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "winged elm"}

  else if(genusSpecies == "Ulmus americana"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "American elm"}

  else if(genusSpecies == "Ulmus crassifolia"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "cedar elm"}

  else if(genusSpecies == "Ulmus rubra"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "slippery elm"}

>>>>

  else if(genusSpecies == "Bourreria sp."){
    taxon_pft_lookup$pft_MRA[i] = "NA"
    taxon_pft_lookup$pft_MODIS[i] = "NA"
    taxon_pft_lookup$phenology[i] = "NA"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "strongbark"
    taxon_pft_lookup$comments[i] = "varied genus"}

@@

  else if(genusSpecies == "Juniperus osteosperma"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen-needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "Utah juniper"
    taxon_pft_lookup$comments[i] = "scale-like needle leaves"}

  else if(genusSpecies == "Juniperus virginiana"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen-needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf" 
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "red cedar"
    taxon_pft_lookup$comments[i] = "scale-like needle leaves"}

@@

  else if(genusSpecies == "Quercus falcata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "southern red oak"}

  else if(genusSpecies == "Quercus geminata"){
    taxon_pft_lookup$pft_MRA[i] = "NA"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "sand live oak"}

  else if(genusSpecies == "Quercus hemisphaerica"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "Darlington oak"
    taxon_pft_lookup$comments[i] = "semi-evergreen or tardily deciduous"}

  else if(genusSpecies == "Quercus laevis"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "turkey oak"}

  else if(genusSpecies == "Quercus laurifolia"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "laurel oak"}

  else if(genusSpecies == "Quercus lyrata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "overcup oak"}

  else if(genusSpecies == "Quercus macrocarpa"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "bur oak"}

  else if(genusSpecies == "Quercus margaretta"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "sand post oak"}

  else if(genusSpecies == "Quercus marilandica"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "blackjack oak"}

  else if(genusSpecies == "Quercus michauxii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "swamp chestnut oak"}

  else if(genusSpecies == "Quercus montana"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "chestnut oak"}

  else if(genusSpecies == "Quercus muehlenbergii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "chinquapin oak"}

  else if(genusSpecies == "Quercus nigra"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "water oak"}

  else if(genusSpecies == "Quercus pagoda"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "cherrybark oak"}

  else if(genusSpecies == "Quercus phellos"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "willow oak"}

  else if(genusSpecies == "Quercus rubra"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "northern red oak"}

  else if(genusSpecies == "Quercus shumardii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "Shumard's oak"}

  else if(genusSpecies == "Quercus sp."){
    taxon_pft_lookup$pft_MRA[i] = "NA"
    taxon_pft_lookup$pft_MODIS[i] = "NA"
    taxon_pft_lookup$phenology[i] = "NA"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "oak"
    taxon_pft_lookup$comments[i] = "varied genus with both deciduous and evergreen species"}

  else if(genusSpecies == "Quercus stellata"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "post oak"}

  else if(genusSpecies == "Quercus velutina"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "black oak"}

  else if(genusSpecies == "Quercus virginiana"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "live oak"
    taxon_pft_lookup$comments[i] = "semi-deciduous"}

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft_MRA[i] = "woody_shrub"
    taxon_pft_lookup$pft_MODIS[i] = "shrub"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "shrub"
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

  else if(genusSpecies == "Rhus aromatica"){
    taxon_pft_lookup$pft_MRA[i] = "woody_shrub"
    taxon_pft_lookup$pft_MODIS[i] = "shrub"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "shrub"
    taxon_pft_lookup$commonName[i] = "fragrant sumac"}

  else if(genusSpecies == "Rhus glabra"){
    taxon_pft_lookup$pft_MRA[i] = "woody_shrub"
    taxon_pft_lookup$pft_MODIS[i] = "shrub"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "shrub"
    taxon_pft_lookup$commonName[i] = "smooth sumac"}

  else if(genusSpecies == "Robinia pseudoacacia"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "black locust"}

  else if(genusSpecies == "Sassafras albidum"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "sassafras"}

  else if(genusSpecies ==  "Sassafras sp."){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "sassafras"}

  else if(genusSpecies == "Sideroxylon lanuginosum"){
    taxon_pft_lookup$pft_MRA[i] = "woody_shrub"
    taxon_pft_lookup$pft_MODIS[i] = "shrub"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "shrub"
    taxon_pft_lookup$commonName[i] = "gum bully"
    taxon_pft_lookup$comments[i] = "deciduous to semi-evergreen"}

  else if(genusSpecies == "Symplocos sp."){
    taxon_pft_lookup$pft_MRA[i] = "NA"
    taxon_pft_lookup$pft_MODIS[i] = "NA"
    taxon_pft_lookup$phenology[i] = "NA"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "sweetleaf"
    taxon_pft_lookup$comments[i] = "varied genus"}

  else if(genusSpecies == "Taxus brevifolia"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen-needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "Pacific yew"}

  else if(genusSpecies == "Tetradium daniellii"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "bee-bee tree"}

  else if(genusSpecies == "Triadica sebifera"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "Chinese tallow"}

  else if(genusSpecies == "Tsuga canadensis"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen-needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "eastern hemlock"}

  else if(genusSpecies == "Tsuga heterophylla"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen-needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "western hemlock"}
